---
title: "Shiny Application and Reproducible Pitch"
author: "Gabriel Lages"
date: "17 de setembro de 2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Slide 1 - Overview

This presentation is part of Cousera Course Project:
Shiny Application and Reproducible Pitch

The focus of the project is explore Data Visualization tools with R.

To visualize the data we created an application with shiny, you can access
the application [here](https://gabrielclages.shinyapps.io/ShinyApp_Fiscal_Study/), or clicking the link below.

Shiny App: https://gabrielclages.shinyapps.io/ShinyApp_Fiscal_Study/ 

You can find more information about the application and all codes that I used on my [github](https://github.com/gabrielclages/ShinyApp_Fiscal_Study)


## Slide 2 - Preparing Data

Currently in Brazil one of the most widely discussed topic in political is the "fiscal pedaling" practiced by the federal government during the year of 2014.

To this study I collected data from [TCU](http://portal.tcu.gov.br/english/home.htm) (The Federal Court of Accounts of Brazil)

First step is to install packages, upload and prepare the dataset

```{r, message=FALSE}
library(dplyr)
library(RCurl)
library(dygraphs)
library(DT)
library(ggplot2)

x <- getURL("https://raw.githubusercontent.com/gabrielclages/Course-Project-Fiscal-Study/master/Dataset_Fiscal_Study.csv")

dataset <- read.csv(text = x, sep = ";", nrows=260)
# Creating a Time Series of the Data 
myts <- ts(dataset$Balance, start=c(1994, 1), end=c(2015, 8), frequency=12)

dataset$Balance <- format(dataset$Balance,justify = "right", big.mark=',', scientific=FALSE)

```

## Slide 3 - Summarizing Data

```{r, message=FALSE}

summary(dataset)

```

## Slide 4 - Time series

This is the time series that we plot and explore in the application

```{r, message=FALSE}
plot(myts)
```

## Slide 5 - Application

To display the understanding of using shiny to build an application, an application has been developed and deployed at: https://gabrielclages.shinyapps.io/ShinyApp_Fiscal_Study/

The application allows the user to:

- Analyze the dataset in an interactive table
- Analyze the brazilian government balance time series in an interactive chart

Read the source at: https://github.com/gabrielclages/ShinyApp_Fiscal_Study